### 2020-05-17 writeup/technical.tex
wip
tl

\section{Main Results: A Model Shift Bias versus Variance Trade-off}\label{sec_denoise}

@@

>>>>

\section{Technical Tools: Quantifying Model Shift Bias versus Variance Trade-off}\label{sec_main}

@@

\section{Extension to Transfer Learning}

We study the transfer function of taskonomy \cite{ZSSGM18}.
The algorithm is as follows.
First, we obtain the single-task estimator $\hat{\beta}_i$ from every task, for $1\le i \le k$.
This forms the shared representation $B$ in Algorithm \ref{alg_estimator}.
Then, we learn the output layer on the target task.
We use our tools to analyze this setting as follows.
